>

### 2024-08-10 docs/article.qmd
Add descriptive tables on daily number of claims

format:
  elsevier-pdf:
    include-in-header:
      file: _header.tex
    journal:
      formatting: review
      cite-style: authoryear
  docx: default

@@

The relational characteristics in health research variables has fueled the growing interest of implementing network analysis, making it an indispensable research framework in medicine and epidemiology [@Luke2007]. Past implementations of network analysis in public health mostly focused on transmission network, social network, and organizational network. Only recently, @Cavallo2012 demonstrated a novel framework to describe medication uses on a population level, i.e. drug prescription network (DPN), a term which later is coined by @Bazzoni2015. Network analysis offers an approach to capture the relationship among building blocks of a complex system. From a health system standpoint, polypharmacy is a prescription of multiple drug combinations which can be further evaluated as a network [@Miglio2021]. DPN is a complex and dynamic system that may change overtime, specifically also in drug prescribed for mental disorders.

@@

Monitoring polypharmacy regimens requires a holistic approach since drug prescription highly depends on the physician's prescribing habits [@Shrivastava2013], patient-physician relationship, and pharmaceutical market, which all bear an interplay with the decision-making process [@Cavallo2012]. A holistic polypharmacy monitoring system needs to describe the importance of polypharmacy by incorporating both qualitative and quantitative measures [@Sirois2016]. Quantitatively attributing importance to each medication is challenging, accounting for polypharmacy as a complex and interlinked medication uses. To reduce the complexity, graph theory offers a complementary approach by analyzing polypharmacy as a DPN. Transforming prescription registry into a DPN has been previously investigated, where DPN-based approach represented the general trend in co-prescription [@Cavallo2012; @Bazzoni2015].

@@

IADB recorded `r n_patient` patients having at least one prescription of antidepressants or anxiolytics within five years of data extraction. The highest average of prescription claim occurred on `r hi_claim$day`, with $\bar{x}$ = `r hi_mean` [`r hi_claim$sd_claim`]. Meanwhile, the lowest average of claim occurred on `r lo_claim$day`, with $\bar{x}$ = `r lo_mean` [`r lo_claim$sd_claim`]. A large margin of difference between the highest and lowest average number of claim implies daily variation and cyclicality, where it peaks on Monday, starts declining afterwards, and is at the lowest during weekends, as shown in figure [-@fig-period-day]. The cyclical patterns are further explained in our supplementary material. @tbl-desc shows the total number of claim for each medication class alongside the distribution of DDD and its weight.

```{r tbl-desc}
#| tbl-cap: Descriptive statistics of prescription data from 2018 to 2022, ordered by the number of claim

tar_read(res_tbl_stat) %>%
  dplyr::arrange(-n_claim) %>%
  dplyr::mutate(
    "mean_sd_dose"      = sprintf("%.2f [%.2f]", dose_mean, dose_sd),
    "median_IQR_dose"   = sprintf("%.2f [%.2f]", dose_median, dose_IQR),
    "mean_sd_weight"    = sprintf("%.2f [%.2f]", weight_mean, weight_sd),
    "median_IQR_weight" = sprintf("%.2f [%.2f]", weight_median, weight_IQR),
    "range_dose"        = sprintf("%.2f - %.2f", dose_min, dose_max),
    "range_weight"      = sprintf("%.2f - %.2f", weight_min, weight_max)
  ) %>%
  subset(select = c(group, n_claim, mean_sd_dose, median_IQR_dose, range_dose, mean_sd_weight)) %>%
  flextable::flextable() %>%
  flextable::set_header_labels(
    group           = "",
    n_claim         = "Claim",
    mean_sd_dose    = "Mean [SD]",
    median_IQR_dose = "Median [IQR]",
    range_dose      = "Range",
    mean_sd_weight  = "Mean [SD]"
  ) %>%
  flextable::add_header_row(
    values    = c("", "Defined Daily Dose", "Weight"),
    colwidths = c(2, 3, 1),
    top       = TRUE
  ) %>%
  flextable::align(align = "center", part = "all") %>%
  flextable::align(j = 1, align = "left", part = "body") %>%
  #flextable::font(fontname = "Times", part = "all") %>%
  flextable::fontsize(size = 7, part = "all") %>%
  flextable::line_spacing(space = 0.7, part = "all")

@@

@@

tar_read(plt_hi_eigen)

@@

- Problem of exposure: Polypharmacy can be defined as cumulative or simultaneous prescriptions
- Cut-off threshold of polypharmacy should be justified by the risk of deleterious health outcomes
- An ideal surveillance system should describe the importance of polypharmacy

>>>>

format:
  elsevier-pdf:
    keep-tex: true
    include-in-header:
      file: _header.tex
    journal:
      formatting: review
      cite-style: authoryear
  docx: default

@@

The relational characteristics in health research variables have fueled the growing implementation of network analysis, making it an indispensable research framework in medicine and epidemiology [@Luke2007]. Past implementations of network analysis in public health mostly focused on transmission network, social network, and organizational network. Only recently, @Cavallo2012 demonstrated a novel framework to describe medication uses on a population level, i.e. drug prescription network (DPN), a term which later is coined by @Bazzoni2015. Network analysis and graph theory offer an approach to model the relationship among building blocks of a complex system. From a complex system standpoint, polypharmacy is a prescription of multiple drug combinations which can be modelled as a network [@Miglio2021]. DPN captures a complex and dynamic system that may vary overtime, which is highly relevant to drug prescribed for mental disorders.

@@

Monitoring polypharmacy regimens requires a holistic approach since drug prescription highly depends on the physician's prescribing habits [@Shrivastava2013], patient-physician relationship, and pharmaceutical market, which all bear an interplay with the decision-making process [@Cavallo2012]. A holistic polypharmacy monitoring system needs to describe the importance of polypharmacy by incorporating both qualitative and quantitative measures [@Sirois2016]. Quantitatively attributing importance to each medication is challenging, accounting for polypharmacy as a complex and interlinked medication uses. To adequately address the complexity, network analysis is a viable framework for analyzing polypharmacy. Transforming prescription registry into a DPN has been previously investigated, where DPN-based approach represented the general trend in co-prescription [@Cavallo2012; @Bazzoni2015].

@@

IADB recorded `r n_patient` patients having at least one prescription of antidepressants or anxiolytics within five years of data extraction. The highest average of prescription claim occurred on `r hi_claim$day`, with $\bar{x}$ = `r hi_mean` [`r hi_claim$sd_claim`]. Meanwhile, the lowest average of claim occurred on `r lo_claim$day`, with $\bar{x}$ = `r lo_mean` [`r lo_claim$sd_claim`]. A large margin of difference between the highest and lowest average number of claim implies daily variation and cyclicality, where it peaks on Monday, starts declining afterwards, and is at the lowest during weekends, as shown in figure [-@fig-period-day]. The cyclical patterns are further explained in our supplementary material. @tbl-desc shows the number of prescriptions for each medication class alongside the distribution of DDD and its weight.

```{r tbl-overview-patient}
#| tbl-cap: "Number of participating patients with at least one claim of antidepressants or anxiolytics from 2018 to 2022"

tar_read(res_tbl_patient) |>
  dplyr::mutate(
    "year"       = as.character(year),
    "Total"      = n_male + n_female,
    "male"       = sprintf("%s (%s)", prettyNum(n_male,   big.mark = ","), scales::percent(p_male)),
    "female"     = sprintf("%s (%s)", prettyNum(n_female, big.mark = ","), scales::percent(p_female)),
    "male_age"   = sprintf("%.2f (%.2f)", age_male, age_sd_male),
    "female_age" = sprintf("%.2f (%.2f)", age_female, age_sd_female)
  ) |>
  dplyr::select(year, male, female, Total, male_age, female_age) |>
  flextable::flextable() |>
  flextable::set_header_labels(
    year       = "Year",
    male       = "Male",
    female     = "Female",
    male_age   = "Male",
    female_age = "Female"
  ) |>
  flextable::add_header_row(
    values    = c("", "Number of Patients (%)", "Mean Age (SD)"),
    colwidths = c(1, 3, 2),
    top       = TRUE
  ) |>
  flextable::align(align = "center", part = "all") |>
  flextable::align(j = 1, align = "left", part = "all") |>
  #flextable::font(fontname = "Times", part = "all") |>
  flextable::fontsize(size = 7, part = "all") |>
  flextable::autofit(add_w = 0, add_h = 0) |>
  flextable::line_spacing(space = 0.7, part = "all")

```{r tbl-overview-daily}
#| tbl-cap: "Daily prescription from 2018 to 2022 among patients with at least one claim of antidepressants or anxiolytics"

res_tbl_overview$overview |>
  dplyr::mutate(
    "mean_sd" = sprintf("%s (%.2f)", prettyNum(mean_claim, big.mark = ","), sd_claim),
    "median_IQR" = sprintf("%s (%.2f)", prettyNum(median_claim, big.mark = ","), IQR_claim),
    "Range" = sprintf("%s - %s", prettyNum(min_claim, big.mark = ","), prettyNum(max_claim, big.mark = ","))
  ) |>
  dplyr::select(day, mean_sd, median_IQR, Range) |>
  flextable::flextable() |>
  flextable::set_header_labels(
    day = "Day",
    mean_sd = "Mean (SD)",
    median_IQR = "Median (IQR)"
  ) |>
  flextable::add_header_row(
    values    = c("", "Number of Claims"),
    colwidths = c(1, 3),
    top       = TRUE
  ) |>
  flextable::align(align = "center", part = "all") |>
  flextable::align(j = 1, align = "left", part = "all") |>
  #flextable::font(fontname = "Times", part = "all") |>
  flextable::fontsize(size = 7, part = "all") |>
  flextable::autofit(add_w = 0, add_h = 0) |>
  flextable::line_spacing(space = 0.7, part = "all")

@@

```{r tbl-desc}
#| tbl-cap: Descriptive statistics of prescription data from 2018 to 2022, ordered by Eigenvector centrality as an indicator of nodal importance

tar_read(res_recon_stat) |>
  dplyr::arrange(-eigen_mean) |>
  dplyr::mutate(
    "mean_sd_eigen"     = sprintf("%.3f [%.3f]", eigen_mean, eigen_sd),
    "median_IQR_eigen"  = sprintf("%.3f [%.3f]", eigen_median, eigen_IQR),
    "mean_sd_dose"      = sprintf("%.2f [%.2f]", dose_mean, dose_sd),
    "median_IQR_dose"   = sprintf("%.2f [%.2f]", dose_median, dose_IQR),
    "mean_sd_weight"    = sprintf("%.2f [%.2f]", weight_mean, weight_sd),
    "median_IQR_weight" = sprintf("%.2f [%.2f]", weight_median, weight_IQR),
    "range_dose"        = sprintf("%.2f - %.2f", dose_min, dose_max),
    "range_weight"      = sprintf("%.2f - %.2f", weight_min, weight_max)
  ) |>
  subset(select = c(group, n_claim, mean_sd_eigen, mean_sd_dose, median_IQR_dose, mean_sd_weight)) |>
  flextable::flextable() |>
  flextable::set_header_labels(
    group            = "",
    n_claim          = "Claim",
    mean_sd_eigen    = "Mean [SD]",
    mean_sd_dose     = "Mean [SD]",
    median_IQR_dose  = "Median [IQR]",
    mean_sd_weight   = "Mean [SD]"
  ) |>
  flextable::add_header_row(
    values    = c("", "Importance", "Defined Daily Dose", "Weight"),
    colwidths = c(2, 1, 2, 1),
    top       = TRUE
  ) |>
  flextable::align(align = "center", part = "all") |>
  flextable::align(j = 1, align = "left", part = "body") |>
  #flextable::font(fontname = "Times", part = "all") |>
  flextable::fontsize(size = 7, part = "all") |>
  flextable::autofit(add_w = 0, add_h = 0) |>
  flextable::line_spacing(space = 0.7, part = "all")

@@

tar_read(plt_hi_eigen_box)

@@

- Problem of exposure: Polypharmacy can be defined as cumulative or simultaneous prescriptions
- Cut-off threshold of polypharmacy should be justified by the risk of deleterious health outcomes
- An ideal monitoring system should describe the importance of polypharmacy
